Practical Open-Loop Optimistic Planning

### 2019-06-11 paper/poster/poster.tex
Updates from Overleaf

We consider the optimal control of an MDP $\cM = (\cS, \cA, R, T, \gamma)$ with bounded rewards $R$
\begin{itemize}
    \item $R$ and $T$ are \hlr{unknown}
    \item Access to a \hlb{generative model} $s' \sim \probability{s'|s,a}$ and $r\sim\probability{r|s, a}$
    \item \hlr{Fixed-budget} setting: the generative model can be queried $n$ times
\end{itemize}
}

@@

\begin{property}[Time and memory complexity]
\begin{equation*}
    \frac{C(\texttt{Lazy KL-OLOP})}{C(\texttt{KL-OLOP})} = \frac{\hleg{nK}}{\hler{K^{L}}}
\end{equation*}
\end{property}

>>>>

We consider the optimal control of an MDP $\cM = (\cS, cA, R, T, \gamma)$ with bounded rewards $R$
\begin{itemize}
    \item $R$ and $T$ are \hlr{unknown}
    \item Access to a \hlb{generative model} $s' \sim \probability{s'|s,a}$ and $r\sim\probability{r|s, a}$
    \item \hlr{Fixed-budget} setting: the generative model can be queried $n$ times
\end{itemize}
}

@@

\begin{property}[Time and memory complexity]
\begin{equation*}
    \frac{C(\texttt{Lazy KL-OLOP})}{C(\texttt{KL-OLOP})} = \frac{\hleg{nA}}{\hler{A^{L}}}
\end{equation*}
\end{property}
